Generalized spaces for constructive algebra

### 2019-09-19 slides-herrsching2019.tex
More work on the slides

>>>>

% \begin{document}

\section{Locales}

\begin{frame}{Locales}
  \begin{hilblock}Locales are a kind of space in which \hil{opens} instead of
  \hil{points} are fundamental.\end{hilblock}

  \begin{columns}[t]
    \begin{column}[t]{0.4\textwidth}
      \textbf{Def.:} A \hil{topological space} consists of a \hil{set of
      points}~$X$ together with a set~$\O(X)$ of point sets which are deemed
      \hil{open} such that unions of XXX
    \end{column}

    \begin{column}[t]{0.6\textwidth}
      \begin{tikzpicture}[sibling distance=8em, level distance=2.5em,
        every node/.style = {shape=rectangle, rounded corners,
          draw, align=center}]
        \node {euclidean spaces} [grow=up]
          child { node {metric spaces}
            child { node {sober topological spaces}
              child { node {locales}
                child { node {toposes}
                  child { node {$\infty$-toposes} } } }
              child { node {topological spaces} } } };
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}
